---
title: "Data and Coding"
author: "Alvin Wendt"
date: "1/7/2021"
output: html_document
---

```{r}
library(leaflet)
library(plotly)
library(dplyr)
library(tidyverse)
library(leaflet.extras)
library(sf)
```


```{r}
service_calls <- read.csv("data/Metro_CFS_OpenData_CLEAN.csv")
```

```{r}
pal <- colorFactor(palette = c("#a6cee3",
"#a6cee3",
"#a6cee3",
"#a6cee3",
"#a6cee3",
"#a6cee3",
"#a6cee3",
"#b2df8a",
"#e31a1c",
"#33a02c",
"#fb9a99",
"#fdbf6f",
"#ff7f00",
"#cab2d6",
"#6a3d9a",
"#6a3d9a",
"#6a3d9a",
"#b15928",
"#ffff99",
"#b15928"),
levels = c("ASLT/BATT NEG INJURY DRIVE-BY SHOOTING",
"ASSAULT/BATTERY",
"ASSAULT/BATTERY NEGATIVE INJURY",
"ASSAULT/BATTERY WITH A GUN",
"ASSAULT/BATTERY WITH OTHER DEADLY WEAPON",
"AUTO BURGLARY",
"BURGLARY",
"FIGHT",
"HOMICIDE",
"INDECENT EXPOSURE",
"JUVENILE DISTURBANCE",
"LARCENY FROM PERSON (NON ROBBERY)",
"MALICIOUS DESTRUCTION OF PROPERTY",
"OTHER DISTURBANCE",
"PERSON WITH A GUN",
"PERSON WITH A KNIFE",
"PERSON WITH OTHER DEADLY WEAPON",
"RECOVERED STOLEN VEHICLE",
"ROBBERY",
"STOLEN MOTOR VEHICLE"))
```

```{r}
leaflet() %>%
  addProviderTiles("CartoDB") %>%
  addMarkers(lng = service_calls$LONG, lat = service_calls$LAT, popup = service_calls$Type_Description, clusterOptions = markerClusterOptions()) 
```


```{r}
SC_map <- service_calls %>% 
  leaflet() %>%
  addProviderTiles("CartoDB") %>%
  addCircleMarkers(radius=2, color = ~pal(Type_Description), popup = service_calls$Type_Description, clusterOptions = markerClusterOptions())
```


```{r}
SC_map %>%
addLegend(position = "bottomright", pal = pal,
values = c("ASLT/BATT NEG INJURY DRIVE-BY SHOOTING",
"ASSAULT/BATTERY",
"ASSAULT/BATTERY NEGATIVE INJURY",
"ASSAULT/BATTERY WITH A GUN",
"ASSAULT/BATTERY WITH OTHER DEADLY WEAPON",
"AUTO BURGLARY",
"BURGLARY",
"FIGHT",
"HOMICIDE",
"INDECENT EXPOSURE",
"JUVENILE DISTURBANCE",
"LARCENY FROM PERSON (NON ROBBERY)",
"MALICIOUS DESTRUCTION OF PROPERTY",
"OTHER DISTURBANCE",
"PERSON WITH A GUN",
"PERSON WITH A KNIFE",
"PERSON WITH OTHER DEADLY WEAPON",
"RECOVERED STOLEN VEHICLE",
"ROBBERY",
"STOLEN MOTOR VEHICLE"))
```

```{r}
service_calls %>% 
  leaflet() %>%
  addProviderTiles("CartoDB") %>%
  addCircleMarkers(
    data = service_calls %>% filter(Type_Description =="OTHER DISTURBANCE"),
    color = ~pal(Type_Description),
    group = "OTHER DISTURBANCE",
    clusterOptions = markerClusterOptions()) %>% 
 addLayersControl(
    overlayGroups = c("OTHER DISTURBANCE"))
```

```{r}
crime_list <- service_calls$Type_Description %>% 
  unique()

```

```{r}
m <- service_calls %>% 
  leaflet() %>%
  addProviderTiles("CartoDB")
for (crime in crime_list){
  m <- m %>% 
    addCircleMarkers(
    data = service_calls %>% filter(Type_Description ==crime),
    color = ~pal(Type_Description),
    group = crime,
    clusterOptions = markerClusterOptions())
}

m <- m %>% addLayersControl(
    overlayGroups = crime_list)
```

```{r}
m
```




```{r}
service_calls %>% 
  pull(Type_Description)
```


```{r}


  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ASLT/BATT NEG INJURY DRIVE-BY SHOOTING",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ASSAULT/BATTERY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ASSAULT/BATTERY NEGATIVE INJURY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ASSAULT/BATTERY WITH A GUN",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ASSAULT/BATTERY WITH OTHER DEADLY WEAPON",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "AUTO BURGLARY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "BURGLARY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "FIGHT",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "HOMICIDE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "INDECENT EXPOSURE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "JUVENILE DISTURBANCE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "LARCENY FROM PERSON (NON ROBBERY)",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "MALICIOUS DESTRUCTION OF PROPERTY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "OTHER DISTURBANCE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "PERSON WITH A GUN",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "PERSON WITH A KNIFE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "PERSON WITH OTHER DEADLY WEAPON",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "RECOVERED STOLEN VEHICLE",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "ROBBERY",
    clusterOptions = markerClusterOptions()) %>%
  addCircleMarkers(
    data = service_calls,
    color = ~pal(Type_Description),
    group = "STOLEN MOTOR VEHICLE",
    clusterOptions = markerClusterOptions()) %>%
    
  addLayersControl(
    overlayGroups = c("ASLT/BATT NEG INJURY DRIVE-BY SHOOTING",
                      "ASSAULT/BATTERY",
                      "ASSAULT/BATTERY NEGATIVE INJURY",
                      "ASSAULT/BATTERY WITH A GUN",
                      "ASSAULT/BATTERY WITH OTHER DEADLY WEAPON",
                      "AUTO BURGLARY",
                      "BURGLARY",
                      "FIGHT",
                      "HOMICIDE",
                      "INDECENT EXPOSURE",
                      "JUVENILE DISTURBANCE",
                      "LARCENY FROM PERSON (NON ROBBERY)",
                      "MALICIOUS DESTRUCTION OF PROPERTY",
                      "OTHER DISTURBANCE",
                      "PERSON WITH A GUN",
                      "PERSON WITH A KNIFE",
                      "PERSON WITH OTHER DEADLY WEAPON",
                      "RECOVERED STOLEN VEHICLE",
                      "ROBBERY",
                      "STOLEN MOTOR VEHICLE"))
```







quakes1 <- quakes[1:10,]

leafIcons <- icons(
  iconUrl = ifelse(quakes1$mag < 4.6,
    "http://leafletjs.com/examples/custom-icons/leaf-green.png",
    "http://leafletjs.com/examples/custom-icons/leaf-red.png"
  ),
  iconWidth = 38, iconHeight = 95,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "http://leafletjs.com/examples/custom-icons/leaf-shadow.png",
  shadowWidth = 50, shadowHeight = 64,
  shadowAnchorX = 4, shadowAnchorY = 62
)

leaflet(data = quakes1) %>% addTiles() %>%
  addMarkers(~long, ~lat, icon = leafIcons)
  
  
  
"ASLT/BATT NEG INJURY DRIVE-BY SHOOTING",
"ASSAULT/BATTERY",
"ASSAULT/BATTERY NEGATIVE INJURY",
"ASSAULT/BATTERY WITH A GUN",
"ASSAULT/BATTERY WITH OTHER DEADLY WEAPON",
"AUTO BURGLARY",
"BURGLARY",
"FIGHT",
"HOMICIDE",
"INDECENT EXPOSURE",
"JUVENILE DISTURBANCE",
"LARCENY FROM PERSON (NON ROBBERY)",
"MALICIOUS DESTRUCTION OF PROPERTY",
"OTHER DISTURBANCE",
"PERSON WITH A GUN",
"PERSON WITH A KNIFE",
"PERSON WITH OTHER DEADLY WEAPON",
"RECOVERED STOLEN VEHICLE",
"ROBBERY",
"STOLEN MOTOR VEHICLE",

```{r}
require(sf)
shapeTracts <- st_read("data/Census Shp File Tracts/cb_2019_us_tract_500k.shp")
shapeGroups <- st_read("data/Census Shp File Groups/cb_2018_32_bg_500k.shp")
```
```{r}
write.csv(shape, "data/Census.csv")
```


